\documentclass[10pt]{amsart}

\usepackage{macros,slashed}

\linespread{1.25}

\usepackage{parskip}
\setlength{\parindent}{18pt}
\setlength{\parindent}{0cm}

\setcounter{tocdepth}{1}

\title{Higher dimensional Kac-Moody symmetries}

\def\brian{\textcolor{blue}{BW: }\textcolor{blue}}
\def\owen{\textcolor{red}{OG: }\textcolor{red}}

\def\q{{\rm q}}
\def\Obs{{\rm Obs}}
\def\ad{{\rm ad}}
\def\cAd{\cA{\rm d}}

\usepackage{tikz}
\usetikzlibrary{arrows,shapes}
\usetikzlibrary{trees}
\usetikzlibrary{matrix,arrows}
\usetikzlibrary{positioning}
\usetikzlibrary{calc,through}
\usetikzlibrary{decorations.pathreplacing}
\usepackage{pgffor}
%\usepackage{tikz-feynman} 

\begin{document}
%\maketitle

\section{Higher Kac--Moody as a boundary theory}

In this section we show how the Kac--Moody factorization algebra appears as the boundary of a twist of supersymmetric gauge theory.

This example extrapolates the ubiquitous relationship between Chern--Simons theory on a $3$-manifold and the Wess-Zumino-Witten conformal field theory.
\brian{expand on this}

The five dimensional gauge theory we consider is obtained as a twist of $\cN=1$ supersymmetric pure gauge theory.
This twist is not topological, but it is holomorphic in four real (two complex) directions, and topological in the transverse direction.
We write down a boundary condition on manifolds of the form $X \times \RR_{\geq 0}$, where $X$ is a Calabi--Yau surface, at $X \times \{0\}$.
Recall, the observables of any theory determine a factorization algebra on the manifold in which the theory lives. 
Likewise, this boundary condition determines a factorization algebra of classical observables supported on the boundary. 
At the classical level, we find that this factorization algebra is the classical limit Kac--Moody factorization algebra on $X$.
We show that there is a quantization of this theory that returns the Kac--Moody at a specified level.  

\begin{rmk} \brian{7d-6d example}
%The seven dimensional theory similarly appears as a twist, this time of maximally supersymmetric gauge theory. 
%We perform a similar analysis to show how to find the higher Kac--Moody on a Calabi--Yau three-fold in the manner sketched above.
\end{rmk}

%\subsection{The $P_0$ structure}
%
%In ordinary classical mechanics, the symplectic structure on the phase space induces the structure of a Poisson algebra on the operators of the theory.
%Classically, the data of a field theory in the BV--formalism involves a $(-1)$-shifted symplectic form on the space of fields. 
%It is shown in \cite{CG2} that this induces the factorization algebra of classical observables with the structure of a strict $P_0$-algebra.
%A $P_0$-algebra is a shifted version of a Poisson algebra in this graded setting.
%Indeed, the data of such an algebra includes a commutative dg product together with a bracket of cohomological degree $+1$. 
%These 
%
%In this section we will describe the $P_0$ structure on the higher dimensional Kac--Moody factorization algebra at level zero. 
%We will give an interpretation of this $P_0$ structure as coming from a Poisson structure on a particular formal moduli space.

%Suppose $\fh$ is any $L_\infty$ algebra. 
%Then, we can define the commutative dg algebra of Chevalley--Eilenberg cochains on $\clie^*(\fh)$. 
%We formulate a convenient way to define homotopy Poisson structures on this commutative dg algebra.  
%The $L_\infty$ algebra $\fh$ acts on $\fh[1]$ via the adjoint representation, and this extends to an action on the completed symmetric algebra $\Hat{\Sym}(\fh[1])$. 
%Consider an element $\Pi \in \clie^*(\fh ; \Hat{\Sym}(\fh[1])$ of total degree $1-n$ \brian{or $n-1$}.
% 
%
%This $P_0$ algebra is induced from a {\em local} Poisson structure on a certain moduli space that we now discuss. 
%
%First, we introduce the following local $L_\infty$ algebra on $X$,
%\ben
%\sL = \Omega^{d,*}_X \tensor \fg [d - 2] \; , \; \; \; \;\; \; \ell_1 = \dbar \tensor \id_{\fg}  , \; \; \; \ell_n = 0 \; \; {\rm for} \; n > 1. 
%\een
%Thus, this an abelian $L_\infty$ algebra concentrated in degrees $-d + 2$ to $2$. 
%
%We have already discussed how local Lie algebras define factorization algebras via the enveloping construction. 
%There is another construction of a factorization algebra that is ``Fourier dual" to this. 
%On an open set $U \subset X$ we assign the complex of Chevalley--Eilenberg cochains on $\sL(U)$, $\clie^*(\sL(U))$.
%The product maps are defined in a natural way. 
%For more details see \brian{ref} in \cite{CG2}. 
%
%For each open $U \subset X$ we have a formal moduli problem $B \sL(U)$ whose functions is commutative dg ring $\clie^*(\sL(U))$. 
%These formal moduli problems glue together to define a {\em local} moduli problem $B \sL$ on $X$ \cite{BY}. 
%The induced factorization algebra of functions on the local moduli problem will be denoted by $\sO(B\sL)$. 

\subsection{$5$d $\cN=1$ supersymmetric gauge theory}
\def\so{\mathfrak{s}\mathfrak{o}}
\def\sl{\mathfrak{s}\mathfrak{l}}

We first provide a description of $5$d $\cN=1$ pure gauge theory. 
The $\cN=1$ supersymmetry algebra in $5$d is of the form
\ben
(\so(5, \CC) \oplus \sl(2, \CC)_R ) \ltimes T_{5{\rm d}}^{\cN = 1}
\een
where $T_{5{\rm d}}^{\cN = 1}$ is the super Lie algebra of $\cN = 1$ supertranslations.
The copy of $\sl(2, \CC)_R$ is the $R$-symmetry Lie algebra.
As a super vector space the supertranslations are
\ben
T_{5{\rm d}}^{\cN = 1} = V_{5{\rm d}} \oplus \Pi (S_{5{\rm d}} \tensor \CC^2_R
\een
where $V \cong \CC^5$ is the fundamental representation of $\so(5, \CC)$ and $S$ is the irreducible spin representation. 
As a complex vector space $S$ is four-dimensional \brian{check that}. 
The $\Pi$ indicates that $S$ is placed in super degree $+1$. 
The only non-trivial Lie bracket in $T_{5{\rm d}}^{\cN = 1}$ is of the form 
\ben
[-,-] : (S_{5{\rm d}} \tensor \CC^2_R) \tensor (S_{5{\rm d}} \tensor \CC^2_R) \to V_{5\d} .
\een
To describe it, introduce the exterior wedge product
\ben
\wedge : S_{5{\rm d}} \tensor S_{5{\rm d}} \to V_{5 \d} . 
\een
where we have used the spin invariant isomorphism $\wedge^2 S_{5{\rm d}} \cong V_{5 \d}$. 
Also, fix the standard holomorphic symplectic pairing $\omega$ on $\CC^2_R$. 
The bracket is defined by $[\psi_1 \tensor v_1, \psi_2 \tensor v_2] = (\psi_1 \wedge \psi_2) \omega(v_1,v_2)$.
The vector multiplet of this algebra consists of a vector, a scalar, and a spinor. 

Let $G$ be a complex algebraic group and $\fg$ its Lie algebra.
The fields of $5\d$ $\cN=1$ pure gauge theory are given by a connection $A$, a scalar $\phi$, and a spinor $\lambda$
\begin{align*}
A & \in \Omega^1 (\RR^5) \tensor \fg \\
\phi & \in C^\infty(\RR^5) \tensor \fg \\
\lambda & \in C^\infty(\RR^5) \tensor (S_{5 \d} \tensor \CC^2_\RR) \tensor \fg .
\end{align*}
The action functional is
\ben
S_{5 \d}^{\cN = 1} (A, \phi, \lambda) = \int_{\RR^6} F(A) \wedge \star F(A) + \lambda \slashed{\partial}_A \lambda + ...
\een 

\begin{prop} \label{prop 5d twist} 
There is a twist of 5d $\cN=1$ supersymmetric pure gauge theory that exists on any manifold of the form $X \times S$ where $X$ is a Calabi--Yau surface and $S$ is a real one-dimensional manifold. 
Choosing local holomorphic coordinates $z_i$ on $X$ and a real coordinate $t$ on $S$, the fields consist of a $\fg$-valued connection one-form
\ben
A = A_{1} \d \zbar_1 + A_2 \d \zbar_2 + A_t \d t \;\;\; , \;\; A_i, A_t \in C^\infty(X \times S) \tensor \fg,
\een 
together with a $\fg^*$-valued one-form
\ben
B = B_1 \d \zbar_1 + B_2 \d \zbar_2 + B_t \d t \;\;\; , \;\; B_i, B_t \in C^\infty(X \times S) \tensor \fg^* .
\een
The action functional is 
\ben
S(A,B) = \int_{X \times \RR} \Omega \left(B \d A + \frac{1}{3} B [A, A] \right)
\een
where $\Omega$ is the holomorphic volume form on $X$. 
\end{prop}

We obtain this result by a dimensional reduction of a twist of 6d $\cN = (1,0)$ pure gauge theory. 

\subsection{$5\d$ $\cN=1$ from $6\d$ $\cN=(1,0)$}

It is known in the literature that $5\d$ $\cN=1$ gauge theory can be obtained from $\cN=(1,0)$ gauge theory in six dimensions via dimensional reduction. \brian{pestun lecture notes. there must be more references though}
At the level of the supersymmetry algebra this is clear to see. \brian{do this} 

In \brian{ref Butson, Costello, Gaiotto} it is shown that there is a holomorphic twist of $6\d$ $\cN=(1,0)$ gauge theory that exists on any Calabi--Yau 3-fold $Y$.
The fields consist of a $(0,1)$-form valued in $\fg$:
\ben
A \in \Omega^{0,1}(Y) \tensor \fg
\een
together with a $(0,1)$-form valued in $\fg^*$:
\ben
B \in \Omega^{0,1}(Y) \tensor \fg^* .
\een
The action functional is
\ben
S^{twist}_{6 \d} (A, B) = \int_Y \Omega_Y \left(\<B, \dbar A\> + \<B, [A,A]\>\right)
\een
where $\Omega_Y$ is the holomorphic volume form on $Y$. 
 
\begin{rmk}
There is a concise geometric description of this twist as an AKSZ type theory.
Let $Y$ be a $3$-fold equipped with a holomorphic volume form as above.
To any holomorphic symplectic manifold $Z$ there is an associated complex three-dimensional AKSZ theory of maps ${\rm Map}(Y,Z)$.
This is holomorphic version of Rozansky--Witten theory, and is spelled out in \cite{QZ}, for instance.
Suppose $\fg$ is the Lie algebra of a complex algebraic group $G$. 
The theory above is holomorphic Rozansky--Witten theory for the (derived) symplectic reduction $* // G$. \footnote{Note that this endows the mapping space ${\rm Map}(Y,Z)$ with a $(-3)$-shifted symplectic structure, as opposed to the familiar $(-1)$-shifted symplectic structure....}
\end{rmk}

We now see how the reduction of this twisted theory from six dimensions down to five dimensions is equal to the description of our $5\d$ theory in Proposition \ref{prop 5d twist}. 
Choose holomorphic coordinates $z_1, z_2, z_3$ on $Y$ and write $z_3 = t + i y$. 
We are reducing along the real $y$-coordinate. 
Write $A = A_1 \d \zbar_1 + A_2 \d \zbar_2 + A_3 \d \zbar_3$ for the theory on $Y$.
In the reduced theory this becomes $A^{5 \d} = A^{5 \d}_1 \d \zbar_1 + A^{5 \d}_2 \d \zbar_2 + A^{5 \d}_t \d t$ where $A_i^{5 \d}$ and $A_{t}^{5 \d}$ are valued in $\fg$. 
Similarly, the $B$ field reduces to $B^{5 \d} = B^{5 \d}_1 \d \zbar_1 + B^{5 \d}_2 \d \zbar_2 + B^{5 \d}_t \d t$. 

Now, consider the quadratic term in the twisted $6\d$ action functional. \brian{finish}...

We have computed the twist of $5\d$ $\cN=1$ at the level of the physical fields. 
We are interested in a refined version of this, that is, a description of the twist of the classical theory in the BV-BRST formalism including the ghosts, anti-fields, etc..

\begin{prop} The holomorphic/topological twist of $5\d$ $\cN=1$ in the BV formalism has space of fields
\ben
(\alpha, \beta) \in \Omega^{0,*}(X) \tensor \Omega^{*}(S) \tensor (\fg \oplus \fg^*) [1],
\een
where $\alpha$ is a form valued in $\fg$ and $\beta$ is a form valued in $\fg^*$. 
The action functional is
\ben
S(\alpha, \beta) = \frac{1}{2} \int \beta (\d_{dR} + \dbar) \alpha \wedge \Omega + \frac{1}{6} \int \beta [\alpha,\alpha] \wedge \Omega
\een
\end{prop}

We will denote the full complex of fields of the $5\d$ gauge theory by $\sE$. 
As is usual in the BV formalism, there is an associated deformation complex consisting of local functionals $\oloc(\sE)$ equipped with the differential $\{S,-\}$.
Cocycles in this complex consist of all the possible deformations of the theory.

There is a deformation that is particularly relevant to finding the Kac--Moody factorization algebra on the the boundary of the $5$-dimensional theory. 
Recall, that an invariant polynomial $\theta \in \Sym^{d+1}(\fg^*)^\fg$ determines a local cocycle of the current algebra on any complex $d$-fold.
When $d=2$ we see that such an element $\theta$ also determines a deformation of the classical gauge theory.

\begin{lem}
Let $\theta \in \Sym^3(\fg^*)^\fg$. 
Define the local functional 
\ben
F_\theta(\alpha,\beta) = \int_{X \times S} \theta(\alpha \partial \alpha \partial \alpha) .
\een
Then, $F_\theta$ defines a deformation of the classical gauge theory.
In other words, the functional $S + F_\theta$ satisfies the classical master equation
\ben
\{S + F_\theta, S + F_\theta\} = 0 .
\een 
\end{lem}

\begin{rmk} It is immediate to check that the degree of $F_\theta$ in $\oloc(\sE)$ is zero.
If we were only writing the part of $F_\theta$ involving the physical fields it would be of the form $\int \theta(A \partial A \partial A)$.
Also, our convention for evaluating $\theta(\alpha\partial \alpha \partial \alpha)$ is the same as above.
We take the wedge product of the form component and evaluate $\theta$ on the Lie algebra component.
\end{rmk}

\subsection{The classical boundary observables}

We now turn to studying the boundary observables of the $5$-dimensional gauge theory introduced in the previous sections. 
We place the theory on a manifold of the form $X \times \RR_{\geq 0}$ where $X$ is a Calabi--Yau
surface.

To specify this classical theory we need to choose a boundary condition at $X \times \RR_{\geq 0}$. 
The space of fields restricted to the boundary is
\ben
\sE^\partial = \Omega^{0,*}(X) \tensor (\fg \oplus \fg^*) [1]
\een
Denote by $\alpha^\partial, \beta^\partial$ the restriction of the fields $\alpha,\beta$ to the boundary. 
Note that space of fields restricted to the boundary is a sheaf of sections of a graded vector bundle on $X$. 
Moreover, $\sE^\partial$ is equipped with a ($0$-shifted) symplectic structure given by
\ben
\omega^\partial(\alpha^\partial, \beta^\partial) = \int_X \alpha^\partial \beta^\partial \Omega .
\een
The boundary condition is given by setting $\alpha|_{X \times \{0\}} = \alpha^\partial = 0$. 
Equivalently, we represent the boundary condition by the Lagrangian subspace
\ben
\sL = \Omega^{0,*}(X) \tensor \fg^* [1] \hookrightarrow \sE^\partial .
\een

\begin{prop}
Consider the $5$-dimensional theory $(\sE, S)$ placed on the manifold $X \times \RR_{\geq 0}$ with $X$ Calabi--Yau.
The factorization algebra of classical boundary observables with respect to the Lagrangian $\sL$ is equivalent to the classical limit of the Kac--Moody factorization algebra on $X$ from \brian{ref}.
\end{prop}

Recall that one can endow the structure of a $P_0$ factorization algebra on the classical limit of the Kac--Moody for every degree one local cocycle of the current algebra.

\begin{prop}
Fix an element $\theta \in {\rm Sym}^{d+1}(\fg^*)^\fg$.
If we turn on the deformation $F_\theta$, the factorization algebra of boundary observables is equivalent as a $P_0$-factorization algebra to the classical limit of the Kac--Moody factorization algebra with $P_0$ structure determined by the local cocycle $J(\theta)$. 
\end{prop}

\brian{Enhancement to arbitrary principal bundle.
Gauge theory will be valued in the adjoint bundle.}

%\subsection{The quantum boundary observables}
%
%We now turn to the quantum observables on the boundary of the $5$-dimensional gauge theory.
%Classically, we have just seen that on the boundary we find the $P_0$-envelope of the current algebra. 
%There is a na\"{i}ve quantization of this $P_0$-envelope given by the factorization enveloping algebra. 
%
%
%\begin{thm}
%There exists an exact one-loop quantization of the holomorphic/topological twist of $5$-dimensional $\cN=1$ gauge theory deformed by the term $F_\theta$ on $\CC^2 \times \RR_{\geq 0}$. 
%The factorization algebra of quantum boundary observables on $\CC^2$ is equivalent to the Kac--Moody factorization algebra $\UU_{\theta_\hbar} (\Omega^{0,*}(\CC^2) \tensor \fg)$ where the $\hbar$-dependent level is
%\ben
%\theta_\hbar = \theta + \# \hbar \ch_{3}^\fg (\fg) \in \Sym^3(\fg^*)^\fg [\hbar] .
%\een
%\end{thm}
%
%\brian{this is analogous to the usual *shift* by the critical level in the quantization of CS/WZW}

%\begin{thm} Consider the twisted theory $\sE_{5d}$ on the manifold $\RR_{\geq 0} \times X$, where $X$ is a Calabi-Yau surface. 
%Then:
%\begin{itemize}
%\item[(1)] there is a boundary condition at $\{0\} \times X$ whose associated degenerate field theory is equivalent to the classical limit of the Kac--Moody factorization algebra on $X$ with {\em WHICH??} $P_0$ structure from Section \ref{sec}, and
%\item[(2)] there exists a one-loop quantization of the $5d$ theory with boundary factorization algebra given by the by the Kac-Moody factorization algebra with level given by the local cocycle corresponding to $\# \ch_3 \in \Sym^3(\fg^*)^\fg$ under the map $J$ above. 
%\end{itemize}
%\end{thm}

%\subsection{Maximally supersymmetric 7d gauge theory}
%
%In this section we will see how the six-dimensional Kac-Moody degenerate field theory arises as the boundary of a supersymmetric gauge theory in seven dimensions.
%
%\begin{prop} The twist of maximally supersymmetric $7d$ pure gauge theory exists on any manifold of the form 
%\ben
%\RR \times X
%\een
%where $X$ is a Calabi-Yau $3$-fold.
%The fields of the theory are
%\ben
%\sE_{7d} = \Omega^{*}(\RR) \tensor \Omega^{0,*}(X) \tensor \fg [\epsilon] [1]
%\een
%where $\epsilon$ is a formal parameter of cohomological degree $-1$.
%If we write the fields as $\alpha + \epsilon \beta$ the action has the form
%\ben
%S(\alpha + \epsilon \beta) = \frac{1}{2} \int \beta (\d_{dR} + \dbar) \alpha \wedge \Omega + \frac{1}{3} \int \left(\beta [\alpha,\alpha] + \alpha [\alpha, \beta]\right) \wedge \Omega .
%\een 
%Here, $\Omega$ is the holomorphic volume form on $X$.
%\end{prop}
%
%\begin{thm} Consider the twisted theory $\sE_{7d}$ on the manifold $\RR_{\geq 0} \times X$, where $X$ is a Calabi-Yau $3$-fold. 
%Then:
%\begin{itemize}
%\item[(1)] there is a boundary condition at $\{0\} \times X$ whose associated degenerate field theory is equivalent to the Kac-Moody on $X$ at level zero with its $P_0$ structure from Section \ref{sec}, and
%\item[(2)] there exists a one-loop quantization of the $7d$ theory with boundary factorization algebra given by the by the Kac-Moody factorization algebra with level given by the local cocycle corresponding to $\# \ch_4 \in \Sym^4(\fg^*)^\fg$ under the map $J$ above. 
%\end{itemize}
%\end{thm}

%\subsubsection{}
%
%The gauge theory we consider arises as a deformation of a partial twist of maximally supersymmetric Yang-Mills gauge theory in seven dimensions. 
%
%\subsubsection{}
%
%\begin{thm} Suppose we put $\Tilde{\cY}_\theta$, the deformation of the twisted $N=2$ gauge theory we considered above, on a 7-manifold of the form $X \times \RR_{\geq 0}$ where $X$ is a Calabi-Yau 6-fold. \owen{You should use the complex dimension rather than the real dimension. Better yet, use less colloquial style, like ``$X$ is a Calabi-Yau manifold of complex dimension 3.''} Then, there is a boundary condition on $X \times \{0\} \subset X \times \RR_{\geq 0}$ whose associated boundary theory is equivalent to the degenerate field theory $\sK_\theta$ on $X$. 
%\end{thm}


\section{Boundary OPE}

We compute the boundary OPE in the presence of the chiral boundary condition of the $5$-dimensional gauge theory we have just discussed.
We restrict ourselves to the manifold $\CC^2 \times \RR_{\geq 0}$, so that the boundary is $\CC^2$. 
By general reasoning, we know that the boundary observables combine to give the structure of a holomorphically translation invariant factorization algebra on $\CC^2$. 

We have seen that such a factorization algebra induces a certain algebraic structure on the cohomology of the local observables, that is, the observables on a small disk $V = \Obs^\q (D^2)$. 
\brian{It may be better to work with the point observables.}
This algebraic structure is encoded by two classes of operations.
First, there is a commutative product
\ben
\cdot : V \tensor V \to V . 
\een 
Second, there is a sequence of $k$-ary brackets, for $k \geq 2$, parametrized by the space $H^{0,?}_{\dbar} ({\rm Conf}_k(\CC^2))$ which take the form
\ben
\Pi_k : V^{\tensor k} \to V \tensor H^{0,?}_{\dbar} ({\rm Conf}_k(\CC^2)) [?] .
\een
In particular, when $k = 2$ we have a binary operation $\Pi_2 : V \tensor V \to V \tensor z_1^{-1} z_2^{-1} \CC [z_1^{-1}, z_2^{1}] [-1]$.
Together, the product and the brackets $\{\Pi_k\}$ make up the higher dimensional OPE for holomorphically translation invariant theories on $\CC^2$. 

\subsection{The local observables}

We have already seen that the classical boundary observables are equivalent to the classical limit of the higher dimensional Kac--Moody factorization algebra. 
Nevertheless, it will be convenient to have explicit representatives for the boundary operators. 

In the presence of our chiral boundary condition, the boundary fields on $\CC^2 \times \{0\} \subset \CC^2 \times \RR_{\geq 0}$ are given by 
\ben
\beta \in \Omega^{0,*}(\CC^2) \tensor \fg^* [1] . 
\een
Fix non-negative integers $n_1,n_2 \geq 0$, a Lie algebra element $M \in \fg$, and a point $z^{(0)} \in \CC^2$. 
Define the linear operator
\ben
O(n_1, n_2 ; M)(w) : \beta \mapsto \partial_{z_1}^{n_1} \partial_{z_2}^{n_2} \<\beta, M\>_{\fg} (z^{(0)}) .
\een 
To read this operator off, we pair the dual Lie algebra part of $\beta$ with $M\in \fg$ to get a smooth function on $\CC^2$. 
Then, we apply the constant coefficient differential operator $\partial_{z_1}^{n_1} \partial_{z_2}^{n_2}$ and evaluate at $z^{(0)}$.
This operator is only defined if $\beta$ is a zero form.
In particular, $O(n_1, n_2 ; M)(z^{(0)})$ has cohomological degree $+1$. 

\brian{Recall the Lemma that the collection $\{O(n_1, n_2 ; M)(z^{(0)})\}$ form a dense subspace of operators on a disk containing $z^{(0)}$.}

For $i = 1,2$ consider the operator 
\ben
\Bar{\eta}_i = \frac{\partial}{\partial(\d \zbar_i)}
\een
acting on the fields $\Omega^{0,*}(\CC^2) \tensor \fg^*[1]$. 
This operator decreases the cohomological degree by one and satisfies 
\ben
[\dbar, \eta_i] = \frac{\partial}{\partial \zbar_i} .
\een
Furthermore, this induces an action on the observables. 
Applied to $O(n_1, n_2 ; M)(z_0)$ we see that
\ben
\Bar{\eta}_i O(n_1, n_2 ; M)(z_0) : \beta^{0,1} \d \zbar^j \mapsto \delta_{ij} \partial_{z_1}^{n_1} \partial_{z_2}^{n_2} \<\beta^{0,1} , M\>_{\fg} (z^{(0)}) .
\een
\brian{I may have missed a sign.}

\subsection{Sourcing the boundary operators}

To compute the boundary OPE we must first find the bulk fields that source the boundary operators. 
For simplicity, we focus on the boundary operators corresponding to $n_1, n_2 = 0$ and denote $O(M)(z^{(0)}) = O(0,0; z^{(0)})$. 

\begin{lem} 
Let $M \in \fg$ and $z^{(0)} \in \CC^2$. 
In the gauge
\ben
Q^{GF} = \dbar^* \tensor 1 + 1 \tensor \d_{dR} ,
\een
the operator $O(M)(z^{(0)})$ sources the is the $\fg$-valued $2$-form field
\ben
\alpha(M)(z^{(0)}) = \alpha(z^{(0)}) \tensor M
\een
where 
\ben
\alpha(z^{(0)}) = \left(\d \zbar_1 \d \zbar_2 \frac{\partial}{\partial t} - \d \zbar_1 \d t \frac{\partial}{\partial z_2} + \d \zbar_2 \d t \frac{\partial}{\partial z_1} \right) \left(t^2 + |z-z^{(0)}|^2 \right)^{-3/2} .
\een
\end{lem}

Similarly, the boundary operator $\eta_i O(M)(z_0)$ is sources the field $\eta_i \alpha (M)(z_0)$. 

\subsection{Holomorphic descent}

Before going in to the calculation of the boundary OPE of the $5$d gauge theory, we set up the general method by which we compute the higher OPE for translation invariant holomorphic theories. 

We suppose we have a theory of the following general form. 
Let $\cV$ be a $\ZZ$-graded \brian{translation invariant} holomorphic vector bundle on $\CC^2$. 
Moreover, suppose that it carries a fiberwise pairing $\<-,-\>_\sV$ of degree $+1$. 
The space of fields of the theory is $\Omega^{0,*}(\CC^2, \sV)$ with $\dbar$ playing the role of the linearized BRST differential. 

The other piece of data of a classical theory is the interaction. 
A translation invariant local functional $I \in \oloc(\Omega^{0,*}(\CC^2, \sV))$ can be written as a sum of functionals of the form
\ben
I(\alpha) = \int_{\CC^2} \d z_1 \d z_2 L(D_1\alpha, \ldots, D_k \alpha)
\een
where $L : \sV^{\tensor k} \to \CC$ is a linear map, and each $D_i$ is a constant coefficient differential operator lying in the space
\ben
\CC\left[\Bar{\eta}_i, \frac{\partial}{\partial \zbar_i}, \frac{\partial}{\partial z_i}\right] .
\een 

\brian{Book shows why CME implies $D_i$ only involve $z$-derivatives.}

\subsubsection{}

Let's first consider the classical observables.

\begin{prop} \brian{cite book}
The classical observables 
\ben
\Obs^{cl} : U \mapsto \left(\sO(\Omega^{0,*}(\CC^2, \sV), \dbar + \{I,-\} \right)
\een
form a holomorphically translation invariant factorization algebra on $\CC^2$. 
\end{prop}

First, we explain how to compute the $z$-dependent brackets using a holomorphic version of descent.  
Suppose $O(z)$ is supported at $z$ and is closed for the classical differential $\d^{cl} = \dbar + \{I,-\}$. 
By translation invariance, we see that $O(z)$ determines a $C^\infty(\CC^2)$-valued observable.
Next, consider the $\Omega^{0,1} (\CC^2)$-valued observable
\ben
O^{(0,1)} = \eta_1 O(z) \d \zbar_1 + \eta_2 O(z) \d \zbar_2 .
\een 
and the $\Omega^{0,2}(\CC^2)$-valued observable
\ben
O^{(0,2)} = \eta_1 \eta_2 O(z) \d \zbar_1 \d \zbar_2 .
\een 
Let $\Tilde{O} = O + O^{(0,1)} + O^{(0,2)}$ be the full $\Omega^{0,*}(\CC^2)$-valued observable.
Observe that $\Tilde{O}$ is closed for the total differential $\dbar + \d^{cl}$. 

To every compact submanifold $K \subset \CC^2$ and element $f(z_1,z_2) \d z_1 \d z_2 \in \d z_1 \d z_2 \CC[z_1,z_2] \subset \Omega^2_{hol}(\CC^2)$ we define the observable
\ben
O_{K,f} = \int_K \Tilde{O} f \d z_1 \d z_2 .
\een 

Now, suppose $O, O'$ are two local observables. 
Let $K = S^3$ and consider the factorization product 
\ben
O (0) \star O'_{S^3, f} .
\een 
This is another local observable, and we assert that it is the image of $\Pi_2(O, O')$ after taking the $S^3$-residue against the function $f$
\ben
\oint_{S^3} \Pi_k(O,O') f \d z_1 \d z_2 .
\een 

\subsection{The boundary OPE}

We now compute the quantum OPE for the boundary of the $5$d gauge theory.
Our calculation is not identical to the calculation for the case of a holomorphic translation invariant theory in the previous section, since the boundary theory we consider is not described by an action functional. 
Nevertheless, the calculation shares many similar traits. 

First, let's consider the tree-level contribution. 

\begin{prop} The tree level contribution to the OPE of the boundary observables of the $5$d gauge theory in the presence of the deformation $F_\theta$ is the same as the OPE for the Kac--Moody factorization algebra on $\CC^2$ at level $\theta \in \Sym^3(\fg^*)^\fg$. 
\end{prop}

\begin{proof}
Let $M_1,M_2 \in \fg$, $z^{(1)}, z^{(2)} \in \CC^2$.
Consider the two operators $O(M_1)(z^{(1)})$ and $O(M_2)(z^{(2)}$ inserted at $z^{(1)}$ and $z^{(2)}$, respectively. 

Suppose first that we turn the deformation off $F_\theta = 0$.
In this case, there is only a single diagram contributing to the tree-level OPE.
\brian{Draw picture.}
It corresponds to the operators propagating into the bulk through their source fields and scattering according to the  term in the action
\ben 
\int_{\CC^2 \times \RR_{\geq 0}} \d z_1 \d z_2  \<\beta, [\alpha, \alpha]\> .
\een 
The resulting boundary operator will be a linear in the field $\beta$. 

This is not quite the way we want to compute the OPE.
In fact, if we perform this naive prescription for calculating the OPE we will get a regular dependence on the difference $z^{(1)} - z^{(2)}$. 
However, this is exactly what we expect from the general theory of holomorphically translation invariant factorization algebras: the cohomological degree zero part of the OPE is commutative. 

To compute the interesting part of the OPE, that is, the degree $-1$ bracket $\Pi_2(O(M_1), O(M_2))$ we must use the method of descent discussed in the previous section. 
(For diagrammatic reasons, at tree level we find $\Pi_k = 0$ for $k > 2$ when the deformation is turned off.)

The prescription for computing this is similar to the case that the holomorphic theory is described by an action functional. 
First, we use the homotopies $\Bar{\eta}_1, \Bar{\eta}_2$ to define the differential form valued observable
\ben
\Tilde{O}(M_1) = O(M_1) + \eta_1 O(M_1) \d \zbar_1 + \eta_2 O(M_1) \d \zbar_2  + \eta_1 \eta_2 O(M_1) \d \zbar_1 \d \zbar_2 .
\een
For the OPE bracket, only the $(0,1)$-part of the observable will be important. 

The fields sourced by $O(M_1)(z^{(1)}, O(M_2)(z^{(2)}$ are $\alpha(z^{(1)}) \tensor M_1, \alpha (z^{(2)} \tensor M_2$ respectively where $\alpha(z)$ is as in Lemma \ref{lem source}. 
The field sourced by $\eta_i O(M_1)$ is $(\eta_i \alpha(z^{(1)})) \tensor M_1$.

It is clear the the Lie algebraic part of the diagram is equal to the bracket $[M_1,M_2]$.
The integral computing the analytic part of the OPE is of the form
\ben
\oint_{z^{(2)} \in S^3} \int_{(z,t) \in \CC^2 \times \RR_{\geq 0}} \d z_1 \d z_2 \alpha(0) \wedge (\Bar{\eta}_1 \alpha(z^{(2)}) \d \zbar_1^{(2)} + \Bar{\eta}_2 \alpha(z^{(2)}) \d z_2^{(2)}) f(z_1^{(1)}, z_2^{(2)}) \d z_1^{(1)} \d z_2^{(2)} .
\een

It is enough to compute
\ben
\int_{\CC^2 \times \RR_{\geq 0}} \d z_1 \d z_2  \alpha(0) \wedge \eta_i \alpha(z^{(2)})
\een
for $i = 1,2$. 
\brian{This is a mess! I think I'm getting something close but I can't simplify a last piece of the argument!}

\end{proof}
\end{document}
