\documentclass[10pt]{amsart}

\usepackage{macros,slashed}

\linespread{1.25}

\usepackage{tikz}
\usetikzlibrary{arrows,shapes}
\usetikzlibrary{trees}
\usetikzlibrary{matrix,arrows}
\usetikzlibrary{positioning}
\usetikzlibrary{calc,through}
\usetikzlibrary{decorations.pathreplacing}
\usepackage{pgffor}

\def\sAd{\sA{\rm d}}

\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{decorations.markings}
\tikzset{
	% >=stealth', %%  Uncomment for more conventional arrows
    vector/.style={decorate, decoration={snake}, draw},
	provector/.style={decorate, decoration={snake,amplitude=2.5pt}, draw},
	antivector/.style={decorate, decoration={snake,amplitude=-2.5pt}, draw},
    fermion/.style={draw=black, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow[draw=black]{>}}}},
    fermionbar/.style={draw=black, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow[draw=black]{<}}}},
    fermionnoarrow/.style={draw=black},
    gluon/.style={decorate, draw=black,
        decoration={coil,amplitude=4pt, segment length=5pt}},
    scalar/.style={dashed,draw=black, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow[draw=black]{>}}}},
    scalarbar/.style={dashed,draw=black, postaction={decorate},
        dwecoration={markings,mark=at position .55 with {\arrow[draw=black]{<}}}},
    scalarnoarrow/.style={dashed,draw=black},
    electron/.style={draw=black, postaction={decorate},
        decoration={markings,mark=at position .55 with {\arrow[draw=black]{>}}}},
	bigvector/.style={decorate, decoration={snake,amplitude=4pt}, draw},
}

\usepackage[final]{pdfpages}

\title{}

\def\opp{{\rm op}}
\def\Ch{{\rm Ch}}
\def\dgLie{{\rm dgLie}}
\def\Lcat{L_\infty{\rm Alg}}
\def\Cur{{\rm Cur}}

\def\brian{\textcolor{blue}{BW: }\textcolor{blue}}


\begin{document}
\maketitle
\tableofcontents

\section{The holomorphic charge anomaly}

For any BV theory $\sE$, the BV operator $\{S,-\}$, which satisfies $\{S,-\}^2 =0$ by the ordinary classical master equation, together with the BV bracket $\{-,-\}$ equip the space of local functionals $\oloc(\sE)$ with the structure of a dg Lie algebra. 
Another way to interpret the equivariant classical master equation is to view $I^{\sL}$ as an element in the dg Lie algebra $\oloc(\sE) \tensor \cloc^*(\sL)$.

This section is mostly a cobbling together of know results above BV quantization for holomorphic theories found in the sources \cite{CG2, BWhol}. 


%\subsection{The quantum master equation} 

Suppose that $\fg$ is an ordinary Lie algebra that exists as a symmetry of a particular classical field theory. 

\subsection{Equivariant holomorphic matter}

We introduce a classical field theory in the BV formalism that one may think of as higher dimensional ``matter" in a holomorphic setting. 
When the complex dimension is one this returns the chiral $\beta\gamma$ system from ordinary conformal field theory. 
In higher dimensions one can also realize this theory as a certain twist of supersymmetric matter. 
First, we motivate in terms of ordinary fields and \brian{not sure}. 

To start, we fix a finite dimensional $\fg$-module $V$ and an integer $d > 0$.
The classical fields of the complex $d$-dimensional theory consist of a map
\beqn\label{gammafield}
\gamma : \CC^d \to V
\eeqn
and a differential form of Hodge type $(d,d-1)$, $\beta \in \Omega^{d,d-1}(\CC^d, V^\vee)$ valued in the dual space $V^\vee$. 
The action functional describing the classical field theory is of the usual form
\beqn\label{actionfnl}
S(\gamma,\beta) = \int \<\beta, \dbar\gamma\>_V
\eeqn
where $\<-,-\>_V$ denotes the natural pairing between $V$ and its dual. 
The classical equations of motion of this theory consist of those $(\gamma,\beta)$ that are holomorphic, namely $\dbar \beta = \dbar \gamma = 0$. 

The gauge symmetry we consider comes from the $\fg$-action on $V$. 
This extends, in a natural way, to an action of the gauge Lie algebra $C^\infty(\CC^d, \fg)$ on the fields (\ref{gammafield}): an element $X(z,\zbar) \in C^\infty(X,\fg)$ acts simply by $X(z,\zbar) \cdot \gamma(z,\zbar)$ where the dot indicates product of functions and the $\fg$-module structure on $V$. 
The condition that this action be compatible with the action functional (\ref{actionfnl}) says precisely that $X(z,\zbar)$ must be holomorphic: $\dbar X(z,\zbar) = 0$. 

When $d=1$ to formulate this theory in the BV formalism we simply...\brian{finish}

\begin{dfn/lem}
The $\sG_d$-equivariant $\beta\gamma$ system on $\CC^d$ with values in $V$ is defined by the local functional
\[
I^{\sG}(\alpha, \beta, \gamma) = \int \<\beta, \alpha \cdot \gamma\>_V \in \oloc(\sE_V \oplus \sG_d[1]) .
\]
This functional satisfies the $\sG_d$-equivariant classical master equation
\[
(\dbar + \d_{\sG}) I^{\sG} + \frac{1}{2} \{I^{\sG}, I^{\sG}\} = 0 .
\] 
\end{dfn/lem}

\subsubsection{The $\beta\gamma$ factorization algebra}

It is the general philosophy of \cite{CG1,CG2} that the observables of a quantum field theory form a factorization algebra on the underlying spacetime. 

%In this section we describe the factorization algebra associated to the higher $\beta\gamma$ system on $\CC^d$ associated to any $\fg$-representation $V$. 

%For any vector space $W$, we can consider the commutative algebra of algebraic and formal algebraic functions denoted respectively by
%\[
%\sO(W) = \Sym (W^\vee) = \bigoplus_{n \geq 0} (W^\vee)^{\tensor n}_{S_n} \;\;\; , \;\;\; \Hat{\sO}(W) = \Hat{\rm Sym}(W^\vee) %= \prod_{n \geq 0} (W^\vee)^{\tensor n}_{S_n} . 
%\] 

For any theory, the factorization algebra of classical observables assigns to every open set $U$ the cochain complex of algebraic functions on the fields supported on $U$.  
For the example of the $\beta\gamma$ system, the differential is just given by the $\dbar$ operator. 
Concretely, the complex of classical observables\footnote{There is also the completed version where one uses $\prod$ in place of $\oplus$ when defining the symmetric algebra, but we will not use it here.} assigned to an open set $U$ is
\[
\Obs^{\cl}_V(U) = \left(\Sym \left(\Omega^{0,*}(U)^\vee \tensor V^\vee \oplus \Omega^{d,*}(U)^\vee \tensor V [-d+1]\right), \dbar\right) .
\]
As usual, we use the completed tensor product when defining the symmetric products. 
It follows from the general results of Chapter 6 of \cite{CG2} that this assignment defines a factorization algebra on $\CC^d$. 

Upon taking global sections, the functional $I^{\sG}$ defines a map of dg Lie algebras $I^{\sG} : \sG_d(\CC^d) \to \Obs^{\cl}_V(\CC^d)$.
We have seen that $\Obs_V^{\cl}$ is a factorization algebra equipped with a $P_0$-structure. 
In the introduction, we also discussed how a local Lie algebra determines a $P_0$-factorization algebra via its classical current algebra. 
The classical Noether's theorem, as proved in Chapter 11 of \cite{CG2}, says that $I^{\sG}$ determines a map between these factorization algebras. 

\begin{prop}{\cite{[CG2]}} (Classical Noether's Theorem)
The assignment that sends an element $\alpha \in \Omega^{0,*}_c(U, \fg)$ to the observable
\[
\gamma \tensor \beta \in \Omega^{0,*}(U, V) \tensor \Omega^{d,*}(U, V^*) \mapsto \int_U \<\beta, \alpha \cdot \gamma\>_V
\]
determines a map of $P_0$-factorization algebras on $\CC^d$
\[
J^{\cl} : \Cur^{\cl} (\sG_d) \to \Obs^{\cl}_V .
\]
\end{prop}

\begin{rmk}
The formula for $J^{\cl}$ is identical to that of the local functional $I^\fg(\alpha)$ defining the action of $\sG_d$ on the $\beta\gamma$ system.
Ordinarily, a local functional does not determine an observable on an open set since the integral may not exist.
However, since $\alpha$ is compactly supported on $U$, it makes sense to restrict $I^\sG (\alpha)$ to an observable on $U$. 
This is precisely the observable $J^{\cl}(\alpha)$. 
\end{rmk}

As always, the statement we are after pertains to the quantum situation. 
Being a free field theory, the $\beta\gamma$ system admits a unique quantization and hence a factorization algebra $\Obs^{\q}_V$ of quantum observables (whose definition we recall below). 
The natural question arises whether the symmetry by the dg Lie algebra $\sG_d$ persists upon quantization. 
We are asking if we can lift $J^{\cl}$ to a ``quantum current" $J^{\q} : \Cur^\q(\sG_d) \to \Obs^\q_V$, where $\Cur^\q(\sG_d)$ is the factorization algebras of quantum currents defined in the introduction. 
The existence of this map of factorization algebras is controlled by the equivariant quantum master equation, which we now turn to.

\subsection{The quantization}

The approach to quantum field theory we use follows Costello's theory of renormalization and the Batalin-Vilkovisky formalism developed in \cite{CosRenorm}.
The formalism dictates that in order to define a quantization, it suffices to define the theory at each energy (or length) scale and to ask that these descriptions be compatible as we vary the scale.
Concretely, this compatibility is through the {\em renormalization group (RG) flow} and is encoded by an operator $W(P_{\epsilon < L}, -)$ acting on the space of functionals. 
The functional $W(P_{\epsilon < L},-)$ is defined as a sum over weights of graphs which is how Feynman diagrams appear in Costello's formalism.
The quantization we work with follows this general approach very closely, with the slight caveat that we are working equivariantly, and so some of the fields are actually background fields. 

The two main ingredients to construct the weight are the propagator $P_{\epsilon < L}$ and the classical interaction $I^{\sG}$. 
The propagator only depends on the underlying free theory, that is, the higher dimensional $\beta\gamma$ system. 
As above, the interaction describes how the linear currents $\sG_d$ act on the free theory. 

Our definition of the propagator $P_{\epsilon<L}$ follows the general approach given in Section ?? of \cite{CG2}.
The construction of $P_{\epsilon<L}$, which makes sense for a wide class theories of this holomorphic flavor, can be found in Section 3.2 of \cite{BWhol}.
For us, it is important to know that $P_{\epsilon<L}$ satisfies the following properties:
\begin{enumerate}
\item[(1)] For $0 < \epsilon < L < \infty$ the propagator is a symmetric element
\[
P_{\epsilon < L} \in \sE_V \Hat{\tensor} \sE_V .
\]
Moreover, $P_{0 < \infty} = \lim_{\epsilon \to 0}\lim_{L \to \infty}$ is a symmetric element of the distributional completion $\Bar{\sE}_V \Hat{\tensor} \Bar{\sE}_V$. 

\item[(2)] 
The propagator lies in the subspace
\[
\Omega^{d,*}(\CC^d \times \CC^d, V \tensor V^*) \oplus \Omega^{d,*}(\CC^d \times \CC^d, V^* \tensor V) \subset \sE_V \Hat{\tensor} \sE_V .
\]
If we coordinatize $(z,w) \in \CC^d \times \CC^d$, the propagator has the form
\beqn
P_{\epsilon<L} = P^{an}_{\epsilon<L}(z,w) \tensor \left({\rm id}_{V} + {\rm id}_{V^*}\right)
\eeqn
where ${\rm id}_V, {\rm id}_{V^*}$ are the elements representing the identity maps which lie in $V \tensor V^*, V^* \tensor V$ respectively. 
Moreover, $P^{an}_{0 < \infty} (z,w)$ is the Green's function for the Hodge Laplacian $\triangle_{\rm Hodge}$ on $\CC^d$:
\[
\triangle_{\rm Hodge} P^{an}_{0<\infty} (z,w) = \delta (z-w) .
\]

\item[(3)] Let $K_t \in C^\infty((0,\infty)_t) \tensor \sE_V \Hat{\tensor} \sE_V$ be the heat kernel for the Hodge Laplacian
\[
\triangle_{\rm Hodge} K_t + \frac{\partial}{\partial t} K_t = 0 .
\]
Then, $P_{\epsilon < L}$ provides a $\dbar$-homotopy between $K_\epsilon$ and $K_L$:
\[
\dbar P_{\epsilon < L} = K_{t=L} - K_{t=\epsilon} .
\]
\end{enumerate}

%The building block in Costello's approach to renormalization is an effective family of functionals $\{I[L]\}$ parametrized by a {\em length scale} $L > 0$. 
%For each $L > 0$ the functional $I[L] \in \sO(\sE)[[\hbar]]$ must satisfy various conditions, which are carefully stated in Definition 8.2.9.1 of \cite{CG2}. 
%We will recall some key aspects that will be useful for our purposes. 
%The main condition is a compatibility between the functionals $I[L]$ as one changes the length scale; this is referred to as {\em homotopy renormalization group (RG) flow}.

To define the quantization, we must recall the definition of a weight of a Feynman diagram adjusted to this equivariant context.
To simplify our discussion, we introduce the notation $\sO(\sG_d[1])$ to mean the underlying graded vector space of $\clie^*(\sG_d)$, so the symmetric algebra on the dual of $\sG_d$. 

For the free $\beta\gamma$ system, the homotopy RG flow from scale $L>0$ to $L'>0$ is an invertible linear map 
\beqn\label{weight1}
W(P_{L < L'} , -) : \sO(\sE) [[\hbar]] \to \sO(\sE)[[\hbar]]
\eeqn
defined as a sum over weights of graphs $W (P_{L<L'}, I) = \sum_{\Gamma} W_{\Gamma}(P_{L<L'}, I)$. 
Here, $\Gamma$ denotes a graph, and the weight $W_\Gamma$ associated to $\Gamma$ is defined as follows.
One labels the vertices of valence $k$ by the $k$th homogenous component of the functional $I$. 
The edges of the graph are labeled by the propagator $P_{L<L'}$.
The total weight is given by iterative contractions of the homogenous components of the interaction with the propagator. 
Formally, we can write the weight as
\[
e^{W(P_{\epsilon <L}, I)} = e^{\hbar \partial_{P_{\epsilon <L}}} e^{I / \hbar}
\]
where $\partial_P$ denotes contraction with $P$. 
For a more precise definition see Chapter 2 of \cite{CosRenorm}.

To define the equivariant version, we extend (\ref{weight1}) to a $\sO(\sG_d[1])$-linear map
\[
W^{\sG} (P_{L < L'} , -) : \sO(\sE \oplus \sG_d[1]) [[\hbar]] \to \sO(\sE \oplus \sG_d[1])[[\hbar]] .
\]
Introduce the weight $W(P_{\epsilon < L}, I^{\sG})$
\begin{dfn/lem}
The prequantization of the $\sG_d$-equivariant $\beta\gamma$ system on $\CC^d$ is defined by the family of functionals $\{I^{\sG}[L]\}_{L > 0}$ where
\beqn\label{prequant}
I^{\sG} [L] = \lim_{\epsilon \to 0} W^{\sG} (P_{\epsilon<L} , I^{\sG}) .
\eeqn 
This family satisfies homotopy RG flow and solves the quantum master equation modulo $\cloc^*(\sG_d)$. 
\end{dfn/lem}

\begin{proof}
The non-trivial claim to justify here is why the $\epsilon \to 0$ limit of $W^{\sG} (P_{\epsilon<L} , I^{\sG})$ exists. 
This follows from the following two claims:

\begin{itemize}
\item[(1)] 
Only one-loop graphs appear in the weight expansion $W^{\sG} (P_{\epsilon < L}, I^{\sG})$. 

\item[(2)] Let $\Gamma$ be a one-loop graph.
Then
\[
\lim_{\epsilon \to 0} W^{\sG}_\Gamma(P_{\epsilon < L}, I^{\sG})
\]
exists.
\end{itemize}

First, we justify claim (1).
Recall that the weight is defined as a sum over {\em connected} graphs.
An immediate consequence of the combinatorics involved in constructing the equivariant weight using the $\beta\gamma$ propagator \brian{finish}. 



\end{proof}



\begin{lem}
For each $L > 0$, the functional $I^{\sG}[L]$ lies in the subspace $\sO(\sE \oplus \sG_d[1]) [\hbar] \subset \sO(\sE \oplus \sG_d[1]) [[\hbar]]$. 
\end{lem}

To define the quantum master equation, we must introduce the BV Laplacian $\Delta_L$ and the scale $L$ BV bracket $\{-,-\}_L$. 
For $L > 0$, the operator $\Delta_L : \sO(\sE_V) \to \sO(\sE_V)$ is defined by contraction with the heat kernel $K_L$ defined above. 
Similarly, $\{-,-\}_L$ is defined by \brian{equation}. 
There are equivariant version of each of these operators by extending via $\sO(\sG_d[1])$-linearity.
For instance, the BV Laplacian is a degree one operator of the form
\[
\Delta_L : \sO(\sE \oplus \sG_d[1]) \to \sO(\sE \oplus \sG_d[1]) .
\]
We say a functional $J \in \sO(\sE_V \oplus \sG_d[1])$ satisfies the scale $L$, $\sG_d$-equivariant quantum master equation if
\[
(\dbar + \d_{\sG}) J+ \frac{1}{2} \{J, J\}_L + \hbar \Delta J = 0 .
\]
The main object of study in this section is the failure for the quantization $I^{\sG}[L]$ to satisfy this equivariant QME. 

\begin{dfn}
The scale $L$, $\sG_d$-equivariant charge anomaly is
\[
\hbar \Theta_V [L] = (\dbar + \d_{\sG}) I^{\sG} [L] + \frac{1}{2} \{I^{\sG}[L], I^{\sG}\}_L + \hbar \Delta I^{\sG}[L] .
\]
As above, $\d_{\sG}$ denotes the Chevalley-Eilenberg differential $\clie^*(\sG_d) = \left(\sO(\sG_d[1]), \d_{\sG}\right)$. 
\end{dfn}

\subsection{The charge anomaly for $\beta\gamma$}

To calculate the anomaly to solving the $\sG_d$-equivariant master equation we utilize a general result about the quantum master equation for holomorphic field theories formulated in \cite{BWhol}. 
In general, since the effective field theory defining the prequantization $\{I^{\sG}[L]\}$ is given by a Feynman diagram expansion, the anomaly to solving the quantum master equation is also given by a potentially complicated sum of diagrams. 
As an immediate corollary of Proposition 4.4 for holomorphic theories on $\CC^d$, we find that only a simple class of diagrams appear in the anomaly. 

The only fields that propagate are the $\beta\gamma$ fields with values in $V$. 
Since all vertices are trivalent we see that the anomaly cocycle is only a functional of the background fields $\sG_d$, see Figure \ref{fig:liewheel}.\footnote{We use squiggly arrows for elements in $\sG$ to be consistent with usual physics conventions for gauge fields.}

\begin{figure}
\begin{center}
\begin{tikzpicture}[line width=.2mm, scale=1.5]

%\pgfmathsetmacro{\ex}{0}
%\pgfmathsetmacro{\ey}{1}

%\draw (\ex,\ey) ++(45:.8) arc (45:-45:.8);

		\draw[fill=black] (0,0) circle (1cm);
		%\draw[fill=red] (0,0) arc (145:215:1);
		\draw[fill=white] (0,0) circle (0.99cm);
		\draw[line width=0.35mm,red] ++(145:0.995) arc (145:215:0.995);
		%\draw[red] (0,0) arc (30:60:3);

		\draw[vector](145:2) -- (145:1);
		\node at (145:2.3) {$\alpha^{(0)}$};
			%\node at (145:0.85) {$v_0$};
		\node at (60:0.75) {$P_{\epsilon<L}$};
		\node at (-60:0.75) {$P_{\epsilon<L}$};
		\draw[vector](215:2) -- (215:1cm);
		\node at (215:2.3) {$\alpha^{(2)}$};
			%\node at (215:0.85) {$v_{d}$};
		\node[red] at (180:0.8) {$K_\epsilon$};
		\draw[vector](0:2) -- (0:1);
		\node at (0:2.3) {$\alpha^{(1)}$};
			%\node at (35:0.85) {$v_{\alpha}$};
		%\node at (0:0.8) {$P_{\epsilon<L}$};
		%\node at (270:0.8) {$P_{\epsilon<L}$};
	    	\clip (0,0) circle (1cm);
\end{tikzpicture}
\caption{The diagram representing the weight $W_{\Gamma, e}(P_{\epsilon<L}, K_\epsilon, I^\sG)$ in the case $d=2$. 
On the black internal edges are we place the propagator $P_{\epsilon < L}$ of the $\beta\gamma$ system. 
On the red edge labeled by $e$ we place the heat kernel $K_\epsilon$.
The external edges are labeled by elements $\alpha^{(i)} \in \Omega^{0,*}_c(\CC^2)$.}
\label{fig:liewheel}
\end{center}
\end{figure}

\begin{lem}\label{lem: obs}
Let $\Theta[L]$ be the obstruction to solving the $\sG_d$-equivariant quantum master equation.
Then, $\Theta := \lim_{L \to 0} \Theta[L]$ exists, and is a local cocycle 
\[
\Theta \in \cloc^*(\sG_d) .
\]
Furthermore, $\Theta$ is computed by the following limit
\[
\hbar \Theta = \frac{1}{2} \lim_{L \to 0} \lim_{\epsilon \to 0} \sum_{\Gamma \in {\rm Wheel}_{d+1} \; , e} W_{\Gamma, e}(P_{\epsilon <L}, K_\epsilon, I^{\sG}) ,
\] 
where the sum is over all wheels of valency $(d+1)$ and internal edges $e$. 
\end{lem}

\begin{rmk}
If $\Gamma$ is a graph with a distinguished edge $e$ and $A,B$ are elements of the tensor square of fields $A, B \in \sE \tensor \sE$, we let $W_{\Gamma,e}(A,B, I)$ denotes the weight of the graph where we place $B$ at the internal edge labeled $e$ and $A$ on the remaining internal edges.
\end{rmk}

In the remainder of this section we will characterize this anomaly algebraically, using the identification of Proposition \cite{prop: trans j}. 
Actually, it is immediate based on symmetry arguments what the obstruction is up to a scalar multiple. 

First, we note that the element $\Theta \in \cloc^*(\sG_d)$ lifts to the invariant subspace of $U(d)$-invariant, holomorphic translation invariant local cocycles.
This follows from the fact that both the functional $I^{\sG}$ and propagator $P_{\epsilon<L}$ are $U(d)$-invariant, holomorphic translation invariant.
By Proposition \ref{prop: trans j} we see that $\Theta$ must be cohomological to a cocycle of the form
\[
(\alpha_0, \ldots, \alpha_d) \mapsto \int_{\CC^d} \theta(\alpha_0 \wedge \partial \alpha_1 \wedge \cdots \wedge \partial \alpha_d) 
\]
where $\theta$ is some element of $\Sym^{d+1}(\fg^*)^\fg$.
In the notation of Section \ref{??}, this is the cocycle $\fJ_d (\theta)$. 
This cocycle factors in the following way:
\beqn\label{composition}
\begin{tikzcd}
\left(\Omega^{0,*}_c(\CC^d) \tensor \fg\right)^{\tensor (d+1)} \ar[r,"\fa \fn"] & \left(\Omega^{0,*}_c(\CC^d) \tensor \fg\right) \tensor \left(\Omega^{1,*}_c(\CC^d)\tensor \fg\right)^{\tensor d} \ar[r, "\theta"] & \Omega^{d, *}_c(\CC^d) \ar[r, "\int"] & \CC . 
\end{tikzcd}
\eeqn
The first map is $\fa \fn : \alpha_0 \tensor \cdots \tensor \alpha_d \mapsto \alpha_0 \tensor \partial \alpha_1 \tensor \cdots \tensor \partial \alpha_d$.
The second map is given by extending the Lie algebraic functional $\theta : \fg^{\tensor (d+1)} \to \CC$ to the Dolbeault complex in the obvious way:
\[
\theta \left(\alpha_0 \tensor (\alpha_1 \tensor \cdots \tensor \alpha_d\right) = \alpha_0 \wedge \theta(\alpha_1 \wedge \cdots \wedge \alpha_d) \in \Omega^{d,*}_c(\CC^d).
\]

Lemma \ref{lem: obs} implies that the obstruction is given by the sum over Feynman weights associated to graphs of wheels of valency $(d+1)$.
We can identify the algebraic component, corresponding to $\theta$ in the above composition (\ref{composition}), directly from the shape of this graph. 
The propagator and heat kernel $P_{\epsilon<L}, K_\epsilon$ labeling the edges factor as
\[
P_{\epsilon<L} = P^{an}_{\epsilon<L} \tensor \left({\rm id}_{V} + {\rm id}_{V^*}\right) \;\; , \;\; K_{\epsilon} = K_{\epsilon}^{an} \tensor \left({\rm id}_{V} + {\rm id}_{V^*}\right)
\]
where ${\rm id}_V, {\rm id}_{V^*}$ are the elements representing the identity maps which lie in $V \tensor V^*, V^* \tensor V$ respectively. 
The analytic factors $P^{an}_{\epsilon<L},  K_{\epsilon}^{an}$ only depend on the dimension $d$. 

Each trivalent vertex of the wheel is also labeled by both an analytic factor and Lie algebraic factor. 
The Lie algebraic part of each vertex can be thought of as the defining map of the representation $\rho : \fg \to {\rm End}(V)$. 
The diagrammatics of the wheel amounts to taking the trace of the symmetric $(d+1)$st power of this Lie algebra factor. 
Thus, the Lie algebraic factor of the weight of the wheel is the $(d+1)$st component of the character of the representation
\[
{\rm ch}_{d+1}^\fg(V) = \frac{1}{(d+1)!} {\rm Tr}\left(\rho(X)^{d+1}\right) \in \Sym^{d+1}(\fg^*) .
\]

By these symmetry arguments, we know that the anomaly will be of the form $\Theta = A \fj (\ch_{d+1}^{\fg}(V))$ for some number $A \in \CC$.
In Appendix \ref{sec: feynman}, we perform an explicit calculation of this constant $A$, which depend on the specific form of the analytic propagator and heat kernel. 

\begin{prop}\label{prop: bg anomaly}
The charge anomaly for quantizing the $\sG_d$-equivariant $\beta\gamma$ system on $\CC^d$ is equal to
\[
\Theta = A  \fj (\ch_{d+1}^{\fg}(V)),
\]
where $\fj$ is the isomorphism from Proposition \ref{prop: trans j}.
\end{prop}

\subsection{Free field realization}

The failure to satisfying the equivariant quantum master equation measures the obstruction to lifting the classical Noether map (\ref{cnoether}) to a map of factorization algebras from the quantum current algebra $\Cur^\q(\sG_d)$. 
The obstruction $\Theta$ to solving the quantum master equation implies that we have a map from the {\em twisted} quantum current algebra. 
As an immediate corollary of Theorem 12.1.0.2 \cite{CG2} we have the following. 

\begin{prop}
Let $\hbar \Theta_V$ be the obstruction to satisfying the $\sG_d$-equivariant quantum master equation. 
There is a map of factorization algebras on $\CC^d$ from the twisted quantum current algebra to the quantum observables
\beqn\label{qnoether}
J^\q : \Cur_{\hbar \Theta_V}^\q (\sG_d) \to \Obs^\q_V 
\eeqn
that fits into the diagram of factorization algebras
\[
\begin{tikzcd}
\Cur^\q_{\hbar \Theta_V} (\sG_d) \ar[d, "\hbar \to 0"'] \ar[r, "J^\q"] & \Obs^\q_V \ar[d, "\hbar \to 0"] \\
\Cur^\cl (\sG_d) \ar[r,"J^\cl"] & \Obs^{\cl}_V .
\end{tikzcd}
\]
\end{prop}

The quantum current algebra $\Cur^\q_{\hbar \Theta_V}$ is a factorization algebra on $\CC^d$ taking values in $\CC[\hbar]$. 
It therefore makes sense to specialize the value of $\hbar$. 
The convention we take is to specialize the value of $\hbar$ to be
\[
\hbar = (2\pi i)^d .
\]

From our calculation of the charge anomaly $\Theta_V$ above, once we specialize $\hbar$ we can realize the current algebra as an enveloping factorization algebra
\[
\left. \Cur^\q_{\hbar \Theta_V} (\sG_d) \right|_{\hbar = (2\pi i)^d} \cong \UU_{\ch_{d+1}^\fg(V)} (\sG_d) .
\]
Thus, as an immediate corollary of the above proposition, $J^\q$ specializes to a map of factorization algebras
\[
J^\q : \UU_{\ch_{d+1}^\fg(V)} (\sG_d) \to \left. \Obs^\q_V \right|_{\hbar = (2\pi i)^d} .
\]

\subsubsection{}

%\begin{cor}
%There is a map of factorization algebras on $\CC^d$, $\Phi^\q : \UU_{\# \ch_{d+1}(\fg^{ad})}(\fg^{\CC^d}) \to \Obs^\q_V$ 
%that fits into the following diagram 
%\[
%\begin{tikzcd}
% \UU_{\# \ch_{d+1}(\fg^{ad})} (\fg^{\CC^d}) \ar[d] \ar[r, dotted, "\Phi^\q"] & \Obs^\q_V \ar[d, "\hbar \to 0"] \\
% \UU (\fg^{\CC^d}) \ar[r, "\Phi^{cl}"] & \Obs^{cl}_V ,
% \end{tikzcd}
% \]
% where $\Phi^{cl}$ is as in Equation (\ref{classicalPhi}). 
% \end{cor}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%% OLD DRAFT BELOW %%%%%%%%%%%%%%%%%%%%%

\appendix

\section{Calculation of the analytic weight} \label{sec: feynman}


\subsection{A module for the higher Kac-Moody}

The last part of this section we diverge to deduce a consequence of the quantum Noether theorem using our analysis above by exhibiting a module for the higher affine algebras from the previous section. 
For convenience, we fix the trivial $\fg$-bundle $P = {\rm triv}$ so that $\sAd(P) = \sG_X$.

On any manifold $X$, the quantum Noether theorem, Theorem 12.1.0.1 of \cite{CG2}, provides a map of factorization algebras
\[
\Phi_X : \UU_\alpha (\sG_X) \to \Obs^\q_{V} ,
\]
for some $\alpha \in H^1_{\rm loc}(\sG_X)$.
The factorization algebra $\Obs^\q_V$ is the quantum observables of the $\beta\gamma$ system on $X$ with values in the $\fg$-module $V$. 
This is a free field theory, thus the above map has the flavor of a {\em free field realization} of the Kac-Moody factorization algebra.
In particular when $X = \CC^d$, or any affine manifold, the calculation above shows that there is a map of factorization algebras
\[
\Phi_{\CC^d} : \UU_{\ch_{d+1}(V)} (\sG_{\CC^d}) \to \Obs^\q_{V} .
\]

Next, consider the case $X = \CC^d \setminus  \{0\}$. 
By functoriality of pushforwards, the quantum Noether theorem produces a map of one-dimensional factorization algebras
\[
\rho_* \Phi : \rho_* \UU_{\ch_{d+1}(V)} (\sG_{\CC^d \setminus \{0\}}) \to \rho_* \Obs^\q_{V} .
\]
We have exhibited a locally constant dense subfactorization algebra $\sF^{lc}_{1d}$ of $\rho_* \UU_\alpha (\sG_X)$ which is equivalent, as an $E_1$-algebra, to $U \Hat{\fg}_{d, \ch_{d+1}(V)}$. 
Similarly, in Section \ref{sec: sphere ops} we have shown that there is a locally constant dense subfactorization algebra that is equivalent to the dg algebra $\sA_V$. 

The map $\rho_* \Phi$ restricts to these dense subfactorization algebras and so defines a map of $E_1$ algebras
\[
\rho_* \Phi : U \Hat{\fg}_{d, \ch_{d+1}(V)}\to \sA_V .
\]
Also, in Section \ref{sec: disk module} we have shown how the disk operators $\sV_V$ form a module, through the factorization product, for the dg algebra $\sA_V$. 
This is essentially the Fock module of the algebra $\sA_V$, thus we should view the above map $\rho_*\Phi$ as being a higher dimensional analog of the ``free field realization" for the higher dimensional affine algebras. 

Further, by induction along the map $\rho_* \Phi$, we obtain the following.

\begin{prop}
The map $\rho_*\Phi$ endows the space $\sV_V$ with the structure of a module over the $E_1$-algebra $U \Hat{\fg}_{d, \ch_{d+1}(V)}$.
Equivalently, $\sV_V$ is an $A_\infty$-module for $U \Hat{\fg}_{d, \ch_{d+1}(V)}$. 
\end{prop}

The module $\sV_V$ is the prototype for a higher dimensional version of the vacuum Verma module for ordinary affine algebras. 
It is enticing to construct the higher excitation Verma modules as dg modules for the higher affine algebras we've considered in this thesis.
We do not do that here, but hope to return to it in future work.

\end{document}