\documentclass[11pt]{amsart}

\usepackage{macros,slashed}

\linespread{1.25}

\def\sAd{\sA{\rm d}}

\usepackage[final]{pdfpages}

\setcounter{tocdepth}{2}

\title{CS in chiral gauge}

%\author{Brian Williams}

\def\brian{\textcolor{blue}{BW: }\textcolor{blue}}
\def\owen{\textcolor{magenta}{OG: }\textcolor{magenta}}

\def\ctensor{\Hat{\tensor}}
\def\Cas{{\sf Cas}}

\newcommand{\changelocaltocdepth}[1]{%
  \addtocontents{toc}{\protect\setcounter{tocdepth}{#1}}%
  \setcounter{tocdepth}{#1}%
}

\begin{document}
\maketitle

Fix a holomorphic volume form on $\Sigma$. 
Typically, when $\Sigma = \CC$ we will pick the form $\d z$. 

In this section, we will work on flat space $\RR^3$ which we will identify with $\CC \times \RR$. 
Choose holomorphic coordinates
\[
(z,\zbar, t) \in \CC \times \RR
\]

The fields of critical Chern-Simons theory are 
\[
(\gamma, \beta) \in \Omega^{0,*}(\CC) \ctensor \Omega^*(\RR) \tensor \fg[1] \oplus \Omega^{0,*}(\CC) \ctensor \Omega^*(\RR) \tensor \fg .
\]
The action is
\[
S(\gamma, \beta) = \int_{\CC \times \RR} \d z \wedge \left(\<\beta, \d \gamma\> + \frac{1}{2} \<\beta, [\gamma,\gamma]\> \right) .
\]

\section{The chiral gauge}

We use the gauge fixing condition
\[
Q^{GF} = \dbar^*_{\CC} + \d_{\RR}^* .
\]
\brian{might need to adjust factors in this equation so that $[Q,Q^{GF}]$ is the standard flat Laplacian in each degree.}
In this gauge, we can write the heat kernel as
\[
K_T ((z,\zbar, t), (w,\wbar, s)) = k_T^{an} ((z,\zbar, t), (w,\wbar, s)) (\d \zbar - \d \wbar) (\d t - \d s) \tensor \Cas_\fg,
\]
where $k_T^{an} \in C^\infty((\CC \times \RR) \times (\CC \times \RR))$, $T > 0$, is the heat kernel for the flat Laplacian on $\RR^3$. 
Explicitly 
\[
 k_T^{an} ((z,\zbar, t), (w,\wbar, s)) = \frac{1}{(4 \pi T)^{3/2}} e^{-|z-w|^2/ 4T - |t-s|^2/4T} . 
 \]

\section{One-loop quantization}

\begin{thm}
Critical Chern-Simons admits a one-loop exact and finite quantization on $\RR^3 = \CC \times \RR$. 
The space of one-loop quantizations is a torsor for the group $H^3_{\rm Lie}(\fg)$.
\end{thm}

\begin{prop}
The following limit 
\[
\lim_{\epsilon \to 0} W(P_{\epsilon < L}, I)
\]
exists for all $L > 0$. 
Thus, in the holomorphic gauge, critical Chern-Simons admits a finite prequantization. 
\end{prop}

\begin{lem}
In the holomorphic gauge, only diagrams of at most one-loop are nonzero in the expansion of $W(P_{\epsilon < L}, I)$. 
\end{lem}

The strategy is to analyze the one-loop diagram by the order of the number of vertices. 
There is a special diagram that could potentially give rise to issues. 

\begin{lem}
Let $\Gamma_2$ be the wheel with two trivalent vertices. 
Then $W_{\Gamma_2}(P_{\epsilon < L}, I) = 0$ identically as a distribution for all $\epsilon , L > 0$. 
\end{lem}
\begin{proof}
Note that the propagator is of the form
\[
P_{\epsilon < L} ((z,\zbar, t), (w,\wbar, s)) = p^{an}_{\epsilon < L} \cdot \left((\d \zbar - \d \wbar) - (\d t - \d s)\right)
\]
where $p^{an}_{\epsilon < L}$ is some smooth function on $(\CC \times \RR)^2$. 
For any fields $\alpha_1,\alpha_2$, the weight $W_{\Gamma_2}(P_{\epsilon < L}, I)(\alpha_1,\alpha_2)$ is given by some integral over $(\CC \times \RR)^2 = \CC_z \times \RR_t \times \CC_{w} \times \RR_s$, but the integrand is proportional to 
\[
P_{\epsilon < L} ((z,\zbar, t), (w,\wbar, s)) \wedge P_{\epsilon < L} ((w,\wbar, s), (z, \zbar, t)) .
\]
This expression is identically zero being the wedge product of proportional one-forms on the same space.
\end{proof}

\begin{lem}
Let $\Gamma_k$ be the wheel with $k$ trivalent vertices. 
Then, for $k > 2$ the limit
\[
\lim_{\epsilon \to 0} W_{\Gamma_k} (P_{\epsilon < L}, I)
\]
exists for all $L > 0$.
\end{lem}

When $\fg$ is semi-simple, one can see in a similar way to the observations made for ordinary Chern-Simons that the obstruction deformation complex guarantees the existence of a quantization of critical Chern-Simons. 
However, we can see that the anomaly for critical Chern-Simons vanishes directly using the holomorphic gauge. 

\begin{lem}
As above, let $\Gamma_k$ denote the wheel with $k$ trivalent vertices. 
When $k=2$, one has
\[
W_{\Gamma_k} (P_{\epsilon < L}, K_\epsilon , I) = 0
\]
identically as a distribution. 
When $k > 2$, then
\[
\lim_{\epsilon \to 0} W_{\Gamma_k} (P_{\epsilon < L}, K_\epsilon , I) = 0 .
\]
\end{lem}

This lemma shows that the one-loop obstruction to solving the quantum master equation of critical Chern-Simons on $\CC \times \RR$ in the holomorphic gauge vanishes for any Lie algebra $\fg$. 
Since the quantization is one-loop exact, this is enough to guarantee a full quantization. 



\end{document}